Double Trouble: Understanding Sex Differences in Synthetic Lethal interactions in Human Cancers \\~\\ Project Updates

### 2023-07-13 july18meeting_pres2/may30ccgmeeting.tex
ppt updates

	\begin{frame}{The Objective}
		\begin{center}
			%\includegraphics[width=11cm, height=6cm]{types_of_courses_taken.jpg}
			Can we build sex-specific synthetic lethality networks for various cancer types? \newline

@@

	%%%%% APPRACH SECTION BEGINS HERE, 2 SLIDES
	\section{Materials \& Methods}

@@

	\begin{frame}{Selection of TCGA Cancer Types}
			\begin{columns}
				\begin{column}{0.45\textwidth}
					\includegraphics[width=5cm, height=8cm]{img3.png}
				\end{column}
				\begin{column}{0.5\textwidth}
					\begin{itemize}
						\item There is a lack of healthy tissue RNA-seq samples in the TCGA database (12 cancers with more than 10 pairs in M and F)
						\item Raw count pan-cancer matrices created with 12 remaining TCGA cancer types (BLCA, COAD, ESCA, HNSC, KICH, KIRC, KIRP, LIHC, LUAD, LUSC, STAD, THCA)
					\end{itemize}
				\end{column}
			\end{columns}			
	\end{frame}

@@

	%Both samples are sequenced at the same depth - sample A has 5 genes expressed at same level, Sample B has the same genes as sample A plus two highly expressed genes that take up 50% of the reads
	\begin{frame}{Normalization for RNA-seq Data Analysis}
		\centering Required to identify genes that are differentially expressed due to some biological phenomena and not due to technical variation
	\end{frame}

@@

	\begin{frame}
		content...
	\end{frame}

	%%%%RESULTS BEGIN HERE
	\section{Results}

>>>>

	\section{Approach}
	\begin{frame}{The Objective}
		\begin{center}
			%\includegraphics[width=11cm, height=6cm]{types_of_courses_taken.jpg}
			Can we build sex-specific synthetic lethality networks for various cancer types? \newline

@@

	%%%%% APPRACH SECTION BEGINS HERE, 2 SLIDES

@@

	\section{Data Collection}
	\begin{frame}{Selection of TCGA Cancer Types}
			\begin{columns}
				\begin{column}{0.45\textwidth}
					\includegraphics[width=5cm, height=8cm]{img3.png}
				\end{column}
				\begin{column}{0.5\textwidth}
					\begin{itemize}
						\item There is a lack of healthy tissue RNA-seq samples in the TCGA database (12 cancers with more than 10 pairs in M and F)
						\item Raw count pan-cancer matrices created with 12 remaining TCGA cancer types (BLCA, COAD, ESCA, HNSC, KICH, KIRC, KIRP, LIHC, LUAD, LUSC, STAD, THCA)
					\end{itemize}
				\end{column}
			\end{columns}			
	\end{frame}

@@

	%Both samples are sequenced at the same depth - sample A has 5 genes expressed at same level, Sample B has the same genes as sample A plus two highly expressed genes that take up 50% of the reads
	\section{Data Processing}
	\begin{frame}{Normalization for RNA-seq Data Analysis}
		\centering Required to identify genes that are differentially expressed due to some biological phenomena and not due to technical variation

		\includegraphics[width=9cm,height=7cm]{img4.png}
	\end{frame}

@@

	\section{Data Processing}
	\begin{frame}{Normal and Tumor Tissue Differ ACROSS 12 Cancer Types}
		\includegraphics[width=12cm, height=6cm]{all_cancerspca_analysis_condition_0.9.png}

		Across all 12 cancer types, the observed variation between healthy and tumor tissue samples is unlikely to have occurred by chance alone (NPManova p-val = 0.0001)
	\end{frame}

	\begin{frame}{Normal and Tumor Tissue Differ WITHIN each Cancer}
		\includegraphics[width=12cm, height=6cm]{all_cancerspca_analysis_condition_cancertype_0.9.png}

		Within each cancer type, the observed variation between healthy and tumor tissue samples is unlikely to have occurred by chance alone (Acceptions: Males: ESCA (LOW SAMPLE SIZE), Females: BLCA, ESCA (LOW SAMPLE SIZE), STAD (LOW SAMPLE SIZE))
	\end{frame}

	\section{Differential Expression}
	\begin{frame}{Finding Differentially Expressed Genes}
		\begin{itemize}
			\item Reads are count based hence they cannot be normally distributed
		\end{itemize}
	\end{frame}
